Cost- and Deadline-Constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-19 paper/paper.tex
Fix missing references

Figure~\ref{fig:budgets} shows the same data for the SIPHT ensemble from another
perspective. It helps answer the question: Given a deadline, how many workflows
can be finished when we increase the budget? In Figure~\ref{fig:budgets}(a) the
growth is super-linear, which results from the Pareto-like distribution of 
workflow sizes in the ensemble (see Figure~\ref{fig:ensemble-distribution}). 
For ensembles of constant size workflows (see Figure~\ref{fig:budgets}(b)) 
the growth is linear and the costs are higher, since all the workflows in the
test consisted of 1000 tasks.

@@

The effect of provisioning delays on workflow performance is similar to that of inaccurate runtime estimates: when the delays are small, all algorithms are able to produce results within the constraints, but when the delays are larger, the dynamic algorithms are able to adapt to avoid exceeding the constraints while the static algorithm is not. The explanation for this behavior is also similar. The difference is that, a very small error in runtime estimates has little impact on the budget, while a very small provisioning delay has a large impact on the budget. Figure~\ref{fig:delays}.a shows that even for an impossibly short provisioning delay of 30 seconds (usually it takes more than than 30 seconds just to boot a VM), the SPSS algorithm exceeds the budget by as much as a factor of 2, and has a distribution with an upper quartile of 1.5 times the budget. In the case of delays more than 5 minutes, which is more typical of what has been observed on academic infrastructure clouds~\cite{Juve2011b} such as Magellan~\cite{Magellan} and FutureGrid~\cite{FutureGrid}, fully three quarters of the simulations exceeded the budget. With the exception of a few outliers for 10 and 15 minute delays, the dynamic algorithms consistently met the budget and deadline constraints.

>>>>

Figure~\ref{fig:budgets} shows the same data for the SIPHT ensemble from another
perspective. It helps answer the question: Given a deadline, how many workflows
can be finished when we increase the budget? In Figure~\ref{fig:budgets}(a) the
growth is super-linear, which results from the Pareto-like distribution of 
workflow sizes in the ensemble (see Figure~\ref{fig:ensemble-pareto}). 
For ensembles of constant size workflows (see Figure~\ref{fig:budgets}(b)) 
the growth is linear and the costs are higher, since all the workflows in the
test consisted of 1000 tasks.

@@

The effect of provisioning delays on workflow performance is similar to that of inaccurate runtime estimates: when the delays are small, all algorithms are able to produce results within the constraints, but when the delays are larger, the dynamic algorithms are able to adapt to avoid exceeding the constraints while the static algorithm is not. The explanation for this behavior is also similar. The difference is that, a very small error in runtime estimates has little impact on the budget, while a very small provisioning delay has a large impact on the budget. Figure~\ref{fig:delays}.a shows that even for an impossibly short provisioning delay of 30 seconds (usually it takes more than than 30 seconds just to boot a VM), the SPSS algorithm exceeds the budget by as much as a factor of 2, and has a distribution with an upper quartile of 1.5 times the budget. In the case of delays more than 5 minutes, which is more typical of what has been observed on academic infrastructure clouds~\cite{Juve2011} such as Magellan~\cite{Magellan} and FutureGrid~\cite{FutureGrid}, fully three quarters of the simulations exceeded the budget. With the exception of a few outliers for 10 and 15 minute delays, the dynamic algorithms consistently met the budget and deadline constraints.
